\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-04-08 paper/paper.tex
bla
Algorithm 2
formatting
Algorithm 1

\usepackage{algorithm}
\usepackage{algpseudocode}

@@

%------------------------------------------------
\section{Algorithms}
\label{app:algs}
\begin{algorithm}
    \begin{algorithmic}[1] % The number tells where the line numbering should start
        \Procedure{BasicColorRefinement}{$G$}
            \While{not stable} \Comment{Worst case loop over every vertex}
            	 \For{every vertex $v \in G(V)$}
            	 	\State calculate neighborhood $nbs$ of $v$
            	  	\If {$nbs$ of $v$ has not changed}
    \State pass
    				\Else
    					\For{every item in the dictionary}
    						\State checks if the configuration is not yet known.
    					\EndFor
    					\If{the configuration is not yet known}
    						\State assign a new color \
    					\EndIf
    				\EndIf
            	  \EndFor
				\For{every vertex in G}
					\State update neighborhood dictionary
				\EndFor
            \EndWhile\label{euclidendwhile}
            \State \textbf{return} stable colored graph
        \EndProcedure
    \end{algorithmic}
    \caption{Basic color refinement}
    \label{euclid}
\end{algorithm}

>>>>

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

%------------------------------------------------
\section{Algorithms}
\label{app:algs}
\begin{algorithm}
    \begin{algorithmic}[1] % The number tells where the line numbering should start
        \Procedure{BasicColorRefinement}{Graph $G(V,E)$, Coloring $C$}
            \While{not stable} \Comment{Worst case loop over every vertex}
            	 \ForAll{$v \in V$}
            	 	\State calculate $v.nbs$ 
            	  	\If{$v.nbs \neq Q[v.class]$} \Comment{nbs is different from previous iteration}
            	  		\If{$v.nbs \in C$} \Comment{New configuration already has a new color}
            	  			\State Assign $v$ this color
            	  		\Else
            	  			\State $v.class = newColor()$
            	  			\State $C$.add($v.class$)            	  		
            	  		\EndIf
    				\EndIf
            	  \EndFor
				\ForAll{$v \in V)$}
					\State update $C[v]$
				\EndFor
            \EndWhile
        \EndProcedure \Comment{Graph $G$ now has a stable coloring}
    \end{algorithmic}
    \caption{Basic color refinement}
    \label{alg:basic}
\end{algorithm}

\begin{algorithm}
    \begin{algorithmic}[1]
    	\Procedure{FastColorRefinement}{$G(V,E)$}
    		\While{$|Q| > 1$}
    			\State $w$ = $Q$.next()
    			\State for $i \geq 0 \in \mathbb{Z}$ let $D_i$ denote the set of $v \in V$ with $i$ neigbours in $w$ 
    			\For{$c \in C \setminus w$}
    				\State let $X_i = D_i \cap c \neq \emptyset$
    				\For{all $X_i$}
    					\If{$max(X) == X_i$}
    						\State $c = X_i$
    					\Else
    						\State add $X_i$ as new class to $C$
    					\EndIf    					
    				\EndFor
    			\If{$c \in Q$}
    				\State $X = X \setminus c$
    			\EndIf
    			\State $Q$.add($X \setminus \max (X$))
    			\EndFor

    		\EndWhile 
        \EndProcedure
    \end{algorithmic}
    \caption{Fast color refinement}
\end{algorithm}
